HPC--101\\Onboarding

### 2020-01-28 hpc_101/sections/04_security.tex
addition of uh filedrop

\subsection{Storing and transmitting data with Google products}
\begin{frame}
  \frametitle{Storing and transmitting data with Google products}
  \onslide<1->{\begin{block}{Question}
    \begin{columns}[T ]
      \begin{column}{0.15\textwidth}\hfill\includegraphics[scale=0.05]{question_mark.png}\end{column}
      \begin{column}{0.80\textwidth}
        Is it safe to store and transmit sensitive or regulated data using the different Google products offerred at the University?
        e.g., Google Docs, Google Drive, Gmail
      \end{column}
    \end{columns}
    \end{block}
    }
  \vfill
  \onslide<2->{\begin{block}{Answer}
%https://www.kissclipart.com/stop-hand-clipart-stop-sign-clip-art-pgay2w/
\begin{columns}
\begin{column}{0.15\textwidth}\hfill\includegraphics[scale=0.05]{stop_hand.png}\end{column}
\begin{column}{0.70\textwidth}
    \centering
    {\HUGE \textbf{\textit{NO!}}}\Large~\\Do \textbf{NOT} store or transmit sensitive or regulated information in \emph{Google Docs}, \emph{Google Drive} or \emph{Email}!
\end{column}
\begin{column}{0.15\textwidth}\includegraphics[scale=0.05]{stop_hand.png}\end{column}
\end{columns}
    \end{block}}
\end{frame}

>>>>

\subsection{Storing and transmitting data with Google products}
\begin{frame}
  \frametitle{Storing and transmitting data with Google products}
  \onslide<1->{\begin{block}{Question}
    \begin{columns}[T ]
      \begin{column}{0.15\textwidth}\hfill\includegraphics[scale=0.05]{question_mark.png}\end{column}
      \begin{column}{0.80\textwidth}
        Is it safe to store and transmit sensitive or regulated data using the different Google products offerred at the University?
        e.g., Google Docs, Google Drive, Gmail
      \end{column}
    \end{columns}
    \end{block}
    }
  \vfill
  \onslide<2->{\begin{block}{Answer}
%https://www.kissclipart.com/stop-hand-clipart-stop-sign-clip-art-pgay2w/
\begin{columns}
\begin{column}{0.15\textwidth}\hfill\includegraphics[scale=0.05]{stop_hand.png}\end{column}
\begin{column}{0.70\textwidth}
    \centering
    {\HUGE \textbf{\textit{NO!}}}\Large~\\Do \textbf{NOT} store or transmit sensitive or regulated information in \emph{Google Docs}, \emph{Google Drive} or \emph{Email}~\\~\\Use the \href{https://www.hawaii.edu/filedrop/}{UH FileDrop} to securely transmit files under 1000 megabytes inside
\end{column}
\begin{column}{0.15\textwidth}\includegraphics[scale=0.05]{stop_hand.png}\end{column}
\end{columns}
    \end{block}}
\end{frame}
